Social Conditions of Fear

### 2023-11-29 scripts/manuscript.qmd
made two summary tables

complete5 <- mice(gss_subset, 
                 m = 5, 
                 seed = 25)

summary(complete(complete5, 1))

temp5 <- complete(complete5, action = "long", include = TRUE)

tidydata_complete <- as.mids(temp5)

save(tidydata_complete, file = "data/tidydata_complete.RData")

@@

```{r}
#| label: descriptive statistics
view(gss_subset)

skimr::skim(gss_subset)

```{r}
#| label: table - gender and fear
gss_subset %>% 
  tabyl(fear, sexnow1) %>% 
  adorn_percentages() %>% 
  adorn_pct_formatting() %>% 
  adorn_ns(position = "front") %>% 
  adorn_title(
    row_name = "Fear at Night",
    col_name = "Gender",
    placement = "combined"
  ) %>% 
  flextable::flextable() %>% 
  flextable::autofit()
```

```{r}
#| label: table - racecombo and fear
gss_subset %>% 
  tabyl(fear, racecombo) %>% 
  adorn_percentages() %>% 
  adorn_pct_formatting() %>% 
  adorn_ns(position = "front") %>% 
  adorn_title(
    row_name = "Fear at Night",
    col_name = "Race",
    placement = "combined"
  ) %>% 
  flextable::flextable() %>% 
  flextable::autofit()
```

```{r}
#| label: fig1-fear_gender
#| fig-cap: Bar graph showing the proportion or respondants, by gender, that feared walking alone at night.

>>>>

#complete5 <- mice(gss_subset, 
 #                m = 5, 
  #               seed = 25)

#summary(complete(complete5, 1))

#temp5 <- complete(complete5, action = "long", include = TRUE)

#tidydata_complete <- as.mids(temp5)

#save(tidydata_complete, file = "data/tidydata_complete.RData")

@@

```{r}
#| label: get to know data more
view(gss_subset)

skimr::skim(gss_subset)
```

```{r}
#| label: descriptive statistics
gss_subset %>% 
  select(fear, sexnow1, racecombo, degree) %>% 
  gtsummary::tbl_summary()
```

```{r}
#| label: tbl_gender_fear
#| tbl-cap: table showing the distribution of fear by gender

gss_subset %>% 
  tabyl(fear, sexnow1) %>% 
  adorn_percentages() %>% 
  adorn_pct_formatting() %>% 
  adorn_ns(position = "front") %>% 
  adorn_title(
    row_name = "Fear at Night",
    col_name = "Gender",
    placement = "combined"
  ) %>% 
  flextable::flextable() %>% 
  flextable::autofit()
```

```{r}
#| label: tbl_racecombo_fear
#| tbl-cap: table showing the distribution of fear by race
gss_subset %>% 
  tabyl(fear, racecombo) %>% 
  adorn_percentages() %>% 
  adorn_pct_formatting() %>% 
  adorn_ns(position = "front") %>% 
  adorn_title(
    row_name = "Fear at Night",
    col_name = "Race",
    placement = "combined"
  ) %>% 
  flextable::flextable() %>% 
  flextable::autofit()
```

```{r}
#| label: fig1-fear_gender
#| fig-cap: Bar graph showing the proportion or respondants, by gender, that feared walking alone at night.
#| message: false
